---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Functions

- `get_bookmaker_json` grab the bookmaker.eu XML feed, download it, convert it to json, then read the json file.
- `nest_bookmaker_json` convert the list object created by reading the json file into a nested dataframe by the `Description` column
- `get_league_desc` get a vector of the unique league/event descriptions. Filter by term, in the example by passing `FUTURES` returning only futures bet types.
- `get_game` pass the nested dataframe and event descritions to unnest the game info.
- `get_future_odds` extract and convert the nested list columns for bets in the future format.


```{r functions}
#library(tidyverse)

get_bookmaker_json <- function(){
  system('curl -sL "http://lines.bookmaker.eu" | xml2json > bkmkr.json')
  jsonlite::fromJSON("bkmkr.json")
}

nest_bookmaker_json <- function(jsonfile){
  jsonfile$Data$Leagues$league %>% 
    as_tibble() %>% 
    group_nest(Description)
}

get_league_desc <- function(df,word){
  desc <- df$Description
  mask <- grepl(x=bkmkr_nest$Description, 
                pattern = word, 
                ignore.case = TRUE)
  desc[mask]
}

get_game <- function(df, desc) {
  df %>%
    filter(Description %in% desc) %>%
    unnest(data) %>%
    unnest(game)
}

get_futures_odds <- function(df){
  df %>% 
    unnest(line) %>% 
    select(prop = htm,
           rot_num = tmnum,
           selection = tmname,
           odds) %>%
    mutate(odds = as.numeric(odds)
    ) 
}
```

## Example

```{r}
# download, convert, load, and nest bookmaker odds
bkmkr_nest <- get_bookmaker_json() %>%
  nest_bookmaker_json()

# get all futures events
futures <- get_league_desc(bkmkr_nest, 'FUTURES')

# extract all events, count the number of items per future/prop
get_game(bkmkr_nest, futures) %>% 
  get_futures_odds() %>% 
  count(prop,sort=TRUE) %>% 
  head(15) %>% 
  knitr::kable()

```

## Stanley Cup Odds

```{r}
get_game(bkmkr_nest, futures) %>% 
  get_futures_odds() %>% 
  filter(prop == 'Odds to Win 2020 - Stanley Cup') %>% 
  distinct() %>% 
  select(-rot_num) %>% 
  knitr::kable()
```


